Social Housing in Toronto

### 2024-04-22 paper/paper.qmd
commit

```{r}
#| label: fig-new-and-housed
#| fig.pos: H
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

```{r}
#| label: fig-total-and-seniors
#| fig.pos: H
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

```{r}
#| label: fig-dependents-or-not
#| fig.pos: H
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

```{r}
#| label: fig-cancelled-vs-total
#| fig.pos: H
#| echo: false
#| eval: true
#| warning: false
#| message: false

>>>>

```{r}
#| label: fig-new-and-housed
#| fig-cap: Yearly New/Reactivated Applications vs. Housed
#| fig.pos: H
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

```{r}
#| label: fig-total-and-seniors
#| fig-cap: Total Active Applications vs. Seniors Applications
#| fig.pos: H
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

```{r}
#| label: fig-dependents-or-not
#| fig-cap: Households with and without Dependents Applying for Social Housing
#| fig.pos: H
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

```{r}
#| label: fig-cancelled-vs-total
#| fig-cap: Inactive/Cancelled vs Total Active Waiting List
#| fig.pos: H
#| echo: false
#| eval: true
#| warning: false
#| message: false
